---
title: "Data analytics in exercise and sport"
subtitle: "<br />Dr Jacquie Tran"
author: "@jacquietran --- ESSA Forum, 4 May 2019"
output:
  xaringan::moon_reader:
    lib_dir: libs
    css: xaringan-themer.css
    nature:
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
      ratio: '16:9'
---

```{r setup, include=FALSE}

options(htmltools.dir.version = FALSE)

# Load libraries ---------------------------------------------------------------

library(here)
library(ghibli)
library(xaringanthemer)

```

```{r xaringan_themer, include = FALSE}

mono_light(
  base_color = ghibli_palette("MononokeDark")[3],
  header_font_google = google_font("Amatic SC", "400b"),
  header_h1_font_size = "80px",
  header_h2_font_size = "60px",
  header_h3_font_size = "50px",
  header_font_weight = "bold",
  text_font_google   = google_font("Montserrat", "400", "400i", "400b"),
  text_font_size = "26px",
  code_font_google   = google_font("Droid Mono"),
  padding = "0em 2em 1em 2em",
  footnote_color = "#666666",
  footnote_font_size = "0.5em",
  footnote_position_bottom = "0.5em"
)

```

class: inverse, center, bottom

# 'Start with the end in mind.'

---

<br />
<br />

What is the decision in need of evidence?

--

How will you make the decision with no additional information?

--

How would you make the decision if you had access to any information you wanted?

--

Can you get access to all the data you ideally want to make your decision?

--

What mistakes are you willing to live with?

--

.footnote[

[1] Argyris, 1976, ['Single-loop and double-loop models in research on decision-making'](http://academic.udayton.edu/richardghere/igo%20ngo%20research/argyris.pdf), _Administrative Science Quarterly_

[2] Byrne, 2018, ['Why Google defind a new discipline to help humans make decisions'](https://www.fastcompany.com/90203073/why-google-defined-a-new-discipline-to-help-humans-make-decisions), _Fast Company_

]

---
class: inverse, center, bottom

# Working with data // Coding with data

---

# Excel: Its power and its pitfalls

--

1. Data, analysis outputs, and visualisation are stored in one place.

--

2. Data is easily manipulated - high risk of introducing errors.

--

3. Point-and-click interface - manual repetition!

--

4. Actions are not logged by default.

--

5. Slow when working with large data sets or files storing many computations.

--

6. Complicated workbooks can 'break' when shared with others.

---

# The case for coding

--

1. Separation of data, analysis outputs, visualisations, and reports.

--

2. Reproducible, transparent, and less error-prone workflow.

--

3. Coding methods are faster for repetitive actions than point-and-click.

--

4. Procedures are documented via scripts and command history.

--

5. Build your own library of frequently used analytical procedures - or use and adapt libraries created by open source developers!

---
class: inverse, center, bottom

# Data analytics in exercise and sport

## A worked example

---

# Section subheader

Slide body text

```{r eval = FALSE, tidy = FALSE}

# Some code I put here for aesthetic purposes ----------------------------------

devtools::install_github("yihui/xaringan")

```

---
class: inverse, center, bottom

# Developing data proficiency

---
class: center, middle

# Thanks!

Slides created via the R package [**xaringan**](https://github.com/yihui/xaringan).